---
title: "p8105_hw1_if2282"
author: Ifrah Fayyaz
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

# Problem 1

## Creating a random sample of size 10, character variable and factor.

```{r, message = FALSE, echo = TRUE, warning = FALSE, results = 'hide'}
prob1_df = 
  tibble(
    samp = rnorm(10),
    gr_than_0 = samp > 0,
    char = c("Apple", "2020", "4", "Fish", "8", "Pigeon", "1999", "Rain", "987", "gr8"),
    fact = factor(c("First", "Second", "Third", "Second", "First", "First", "Third", "First", "Second", "Second"))
  )
mean(pull(prob1_df, samp))
mean(pull(prob1_df, gr_than_0))
mean(pull(prob1_df, char))
mean(pull(prob1_df, fact))
```
Only the mean for "samp" variable works since it is a numeric variable. The mean for the logical, character and factor variables is not generated and I am given a warning message.


## Taking means for logical, character and factor variables:

```{r, echo = TRUE, warning = FALSE, results = 'hide'}
gr_than_0.n = mean(as.numeric(pull(prob1_df, gr_than_0)))
char.n = mean(as.numeric(pull(prob1_df, char)))
fact.n = mean(as.numeric(pull(prob1_df, fact)))
```
After applying as.numeric, we obtained mean for all the variables. I got a numeric mean for my factor variable and that is because my elements got converted to numbers - "first" got converted to 1 etc. For the character variable, I got the mean as 'NA_real_' and that is because even after converting its type to numeric, the elements were not numeric.











