---
title: "p8105_hw1_if2282"
author: Ifrah Fayyaz
output: 
  github_document:
    toc: TRUE
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

# Problem 1

## Creating a random sample of size 10, character variable and factor.

```{r, message = FALSE, echo = TRUE, warning = FALSE}
prob1_df = 
  tibble(
    samp = rnorm(10),
    gr_than_0 = samp > 0,
    char = c("Apple", "2020", "4", "Fish", "8", "Pigeon", "1999", "Rain", "987", "gr8"),
    fact = factor(c("First", "Second", "Third", "Second", "First", "First", "Third", "First", "Second", "Second"))
  )
mean(pull(prob1_df, samp))
mean(pull(prob1_df, gr_than_0))
mean(pull(prob1_df, char))
mean(pull(prob1_df, fact))
```
I obtain the mean for "samp" and "gr_than_0" variables but the mean for the character and factor variables is not generated and I am given a warning message.


## Taking means for logical, character and factor variables:

```{r, echo = TRUE, warning = FALSE, results = 'hide'}
mean(as.numeric(pull(prob1_df, gr_than_0)))
mean(as.numeric(pull(prob1_df, char)))
mean(as.numeric(pull(prob1_df, fact)))
```
After applying as.numeric, we obtained mean for all the variables. I got a numeric mean for my factor variable and that is because my elements got converted to numbers - "first" got converted to 1 etc. For the character variable, I got the mean as 'NA_real_' and that is because even after converting its type to numeric, the elements were not numeric.

# Problem 2

```{r, echo = FALSE, message = FALSE}
data("penguins", package = "palmerpenguins")
```

## Penguin Data Description

The penguin data set has the following variables: `r names(penguins)`. The types of penguins are `r levels(pull(penguins, species))` and the types of islands are `r levels(pull(penguins, island))`. The total number of rows in the dataset are `r nrow(penguins)` and the number of columns are `r ncol(penguins)`. The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm.

## Scatterplot for Bill Length vs. Flipper Length

```{r, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatterplot.pdf", height = 8, width = 12)
```


